### 2014-10-30 paper/system_overview.tex
adding a table for api

\subsection{API}
In this section, we explain our API which can be used to define custom events, processes and adapters. We provide clear interfaces to abstract out all the communication complexities from application developers.

@@

\begin{lstlisting}
public interface Event {
    String getKey();
    void serialize(DataOutput dataOutput);
    void parse(DataInput dataInput);
}

public interface Element {
    void initialise(Container container,
            Map<String,String> parameters);
}

public interface Adaptor extends Element {
    void start();
}

public interface Processor extends Element {
    void onEvent(Event event);
}
\end{lstlisting}

>>>>

\subsection{API}
In this section, we explain our API which can be used to define custom events, processes and adapters. We provide clear interfaces to abstract out all the communication complexities from application developers. Table \ref{api} shows details of client interfaces.

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{| l | l | l |}
        \hline
        Interface Name &  Method & Parameters \\
        \hline
        Event   & getKey &  \\
        \cline{2-3}
        & serialize &  DataOutput \\
	\cline{2-3}        
        & parse &  DataInput \\
        \hline
        Adaptor   & start &  \\
        \cline{2-3}
        & initialise &  Container \\
        \hline
        Processor   & onEvent & Event \\
        \cline{2-3}
        & initialise &  Container \\
        \hline
        \end{tabular}
        \caption{Client API}
        \label{api}
\end{table}
